\documentclass[a4paper,10pt]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{microtype}
\pagestyle{empty}

\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1.0}
\setlist[itemize]{topsep=2pt,itemsep=1pt,leftmargin=0.15in}
\titleformat{\section}{\scshape\small\raggedright}{}{0em}{}[\titlerule]

\newcommand{\resumeSub}[4]{%
  \item \textbf{#1} \hfill {#2} \\
        {#3} \hfill {#4}
}

\begin{document}

% ---------- Header ----------
\begin{center}
    {\Large \bfseries Poreddy Chakradhar Reddy} \\
    Hyderabad, India \quad | \quad +91 8520864129 \\
    \href{mailto:chakrip24@gmail.com}{chakrip24@gmail.com} \quad | \quad 
    \href{https://github.com/Drax-dr}{github.com/Drax-dr} \quad | \quad
    \href{https://linkedin.com/in/chakradhar-reddy-879040235}{linkedin.com/in/chakradhar-reddy-879040235}
\end{center}

% ---------- Summary ----------
\section{Professional Summary}
\begin{itemize}
    \item Full-stack developer experienced in secure, scalable web applications and backend systems using Go, Python, and JavaScript.
    \item Skilled in REST API development, containerization, system design, and cryptographic protocol implementation.
    \item Passionate about privacy-first infrastructure, backend architecture, and DevSecOps practices.
\end{itemize}

% ---------- Technical Skills ----------
\section{Technical Skills}
\begin{itemize}
    \item \textbf{Languages:} Go, Python, JavaScript, TypeScript
    \item \textbf{Frameworks:} Flask, FastAPI, Fiber, React, Tailwind CSS
    \item \textbf{Tools:} Docker, GitHub, Postman, Podman, Docker Compose
    \item \textbf{Database:} SQLite, PostgreSQL (basic), MongoDB (basic)
    \item \textbf{Security:} JWT, OAuth2, NaCl, ChaCha20-Poly1305, HTTPS, secure API design
\end{itemize}

% ---------- Education ----------
\section{Education}
\begin{itemize}
    \resumeSub{Bachelor of Technology in Computer Science and Engineering}{2022–2026}{Malla Reddy Engineering College, Hyderabad}{}
    \resumeSub{Intermediate - MPC (82.1\%)}{2020–2022}{Narayana Junior College, Hyderabad}{}
    \resumeSub{High School (CGPA: 10.0)}{Completed}{Sri Chaitanya Techno School, Hyderabad}{}
\end{itemize}

% ---------- Projects ----------
\section{Projects}
\begin{itemize}
    \item \textbf{Encrypt API} — Go, Fiber  
    \begin{itemize}
        \item Secure encryption microservice for text and files using ChaCha20-Poly1305.
        \item RESTful design, JWT integration, NaCl primitives.
        \item \href{https://github.com/Drax-dr/encrypt-api}{github.com/Drax-dr/encrypt-api}
    \end{itemize}

    \item \textbf{Basic Blog App} — Python, Flask  
    \begin{itemize}
        \item Blog platform with SQLite, Flask-Login, Semantic UI, Dockerized.
        \item 500+ Docker pulls; built using modular structure.
        \item \href{https://github.com/Drax-dr/blog}{github.com/Drax-dr/blog}
    \end{itemize}

    \item \textbf{Blog API Service} — Flask RESTful API  
    \begin{itemize}
        \item JWT-secured backend with CRUD routes and Flask-Admin UI.
        \item Decoupled blog logic from frontend.
        \item \href{https://github.com/Drax-dr/blog-api}{github.com/Drax-dr/blog-api}
    \end{itemize}
\end{itemize}

% ---------- Soft Skills ----------
\section{Soft Skills}
\begin{itemize}
    \item Problem-solving, critical thinking, fast learner, attention to detail, communication, self-motivation, teamwork
\end{itemize}

% ---------- Interests ----------
\section{Interests}
\begin{itemize}
    \item Secure APIs, privacy-focused apps, cryptography, backend architecture, developer tools, self-hosting, red teaming, blockchain security
\end{itemize}

\end{document}
